\sysfull

### 2017-08-04 paper/evaluation.tex
Text added describing result on page swaps (needs second iteration)

\begin{table}[t]
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Cold chain & 388 & 721 \\ %53\%
		Cuckoo & 483 & 762 \\ %63\%
		RSA & 887 & 1233 \\ %71\%
		Bitcount & 351 & 588 \\ %59\%
		DFT & --- & --- \\ %Two resolutions: 4 and 8 Bytes
		Huffman & --- & --- \\ %Data decompression size: 100 bytes
		Selection sort & --- & --- \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\caption{Initial figure about page size overhead. \todo{Figure placeholder---will be replaced with final one}{Amjad}}
	\label{fig:IPOSPerformance}
\end{figure}

@@

Expected results:
\begin{itemize}
	\item Sensitivity plot---normalized page swapping cost ("bathtub" curve) in terms of execution time: compare against Chain and full double buffering approach; show number of page swaps---do the experiment for all applications
\end{itemize}

\todo{Provide argument for page swapping using hardware support}{Brandon}

>>>>

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Cold chain & 388 & 721 \\ %53\%
		Cuckoo & 483 & 762 \\ %63\%
		RSA & 887 & 1233 \\ %71\%
		Bitcount & 351 & 588 \\ %59\%
		DFT & --- & --- \\ %Two resolutions: 4 and 8 Bytes
		Huffman & --- & --- \\ %Data decompression size: 100 bytes
		Selection sort & --- & --- \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\caption{Page size overhead.\todo{Figure placeholder---will be replaced with final one}{Amjad}}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}

Figure~\ref{fig:page_size} presents the result on the effect of page swap size on the execution time of the programs executed by \sys. Overhead has been measured in the MCU clock cycles\todo{WISP? EDB? CCS?}{Amjad}. Result has been normalized \todo{To what?}{Amjad}. A subset of applications has been selected for evaluation. Additionally, page faults have been measured. \todo{Comparison with Chain and double buffering?}{Amjad} The result show clearly a bathtub-shape bar plot for each application, demonstrating that for each application there is always a page size that minimizes \emph{both} execution time and page swaps. For all applications (except for Sort) this value equals to 64 pages\todo{And one page is?}{Amjad}. The shape of each figure can be explained as follows. For small page swaps (<64) the execution time is dominated by the \emph{frequency} of page swaps (each swap takes time, as shown in Figure~\ref{fig:dmaTimeEnergy}). On the other hand, in the opposite case execution time is dominated by the time of swapping one large page. Another interesting observation is the non-symmetric shape of the bar plot.\todo{Why do we see non-symmetry}{Amjad}
